Funding programmes for early career researchers do/not influence their independence

### 2023-09-13 article.Rmd
data collection complete

To check whether we can use "the most frequent co-author of the first 5 publications" as a proxy to identify supervisors, we have compared the supervisors identified via this method with the manually found supervisors for each researcher in our sample.
In the treatment group of `r nrow(tar_read(ids_complete))`researchers,  118 (49 %) had their most frequent co-author same as their supervisor and 86 (36 %) had someone other than their supervisor as their most frequent co-author in their first 5 publications, and 37 (15%) had no co-author in their first 5 publications.  
In the control groups, we have manually found supervisors for `r nrow(tar_read(sup_control) %>% filter(!is.na(sup_vedidk)) %>% distinct(name_first, name_last))` researchers, and when we compared them to the supervisors suggested by the most frequent coauthor algorithm, we found that 41 (29 %) had their most frequent co-author the same as their supervisor, 80 (57 %) had someone other than their supervisor as their most frequent co-author in their first 5 publications, and 20 (14 %) had no co-author in their first 5 publications.

>>>>

To check whether we can use "the most frequent co-author of the first 5 publications" as a proxy to identify supervisors, we have compared the supervisors identified via this method with the manually found supervisors for each researcher in our sample.
In the treatment group of `r nrow(tar_read(ids_complete))`researchers,  118 (49 %) had their most frequent co-author same as their supervisor and 86 (36 %) had someone other than their supervisor as their most frequent co-author in their first 5 publications, and 37 (15%) had no co-author in their first 5 publications.  
In the control groups, we have manually found supervisors for `r nrow(tar_read(sup_complete) %>% filter(!is.na(sup_vedidk)) %>% distinct(name_first, name_last))` researchers, and when we compared them to the supervisors suggested by the most frequent coauthor algorithm, we found that 41 (29 %) had their most frequent co-author the same as their supervisor, 80 (57 %) had someone other than their supervisor as their most frequent co-author in their first 5 publications, and 20 (14 %) had no co-author in their first 5 publications.
